---
title: 'test'
output:
  html_document:
    pandoc_args: "--dpi=200"
    fig_height: 3
    fig_width: 5
    code_folding: show
    df_print: kable
    toc: true
    toc_depth: 3
    toc_float: true
editor_options: 
  chunk_output_type: console
---


Hi! Here are some words.


# A heading  
\
\
I usually run this chunk with the option `echo=FALSE` and use this chunk to display some standard info about the analysis, almost like a header at the top of the document.  Since I have this issue with `DT::datatable()` regardless of the chunk settings, I decided to leave the code visible in the markdown report.

\

As you can see, in this chunk, `DT::datatable()` renders just fine.  

\



```{r}


df1 = data.frame(
  df = 111,
  "Date Submitted" = "1/1/1999",
  "Date Required" = "1/1/2020",
  Description = "words",
  "Link to File/Folder" = "hre/here/there",
  "Approx Time Needed?" = NA, 
  Requestor = "Me"
)



DT::datatable(df1, 
							extensions = "Buttons",
							rownames = F, 
							options = list(dom = 'B',
														 scrollX = TRUE,
														 buttons = list(list(extend = 'copy', 
														 										title = NULL, 
														 										header = FALSE))) )




```

\
\
\
\



# My usual setup

I use this section to load some packages, source some custom scripts, and to import and clean the data, etc.

```{r}
rm(list = ls())
knitr::opts_chunk$set(echo = TRUE, results = "asis")
suppressMessages(library(tidyverse))
suppressMessages(library(tidylog))
suppressMessages(library(data.table))
suppressMessages(library(DT))


df2 = data.frame(x = 1:5,
								 y = 6:10
								 )

```





\
\
\
\

# Calculations  

This is were the fancy data wizardry usually happens.

```{r}

df2$z = df2$x + df2$y

```



\
\
\
\


# Results  

\

I (try to) report the results here.  For some reason though, `DT::datatable()` won't render the results anymore.


```{r}





DT::datatable(df2, 
							extensions = "Buttons",
							rownames = F, 
							options = list(dom = 'B',
														 scrollX = TRUE,
														 buttons = list(list(extend = 'copy', 
														 										title = NULL, 
														 										header = FALSE))) )




```


\
\

It still won't render the results even if I use the default options:

```{r}
DT::datatable(df2)
```


\
\
\
\



# Session info

```{r}

pander::pander(sessionInfo())

```
